Probabilistic Forward Modeling of Galaxy Catalogs with Normalizing Flows

### 2023-11-28 src/tex/ms.tex
Fixed latex typo

For the training set, we use 100,000 galaxies from the catalog created in Section~\ref{sec:galaxy-catalog}.
Each galaxy in the training set has a true redshift and observed magnitudes in the $ugrizy$ bands, with corresponding photometric errors.
To account for the photometric error, at the start of each training epoch, we resample the training set from the photometric error distributions.
In other words, each epoch, for each galaxy, we sample
\begin{align}
    \mathbf{m} \sim p(\mathbf{\hat{m}}, \mathbf{\sigma_m}),
\end{align}
where $\mathbf{\hat{m}}$ are the observed magnitudes with photometric errors $\mathbf{\sigma_m}$, and $p(\mathbf{\hat{m}}, \mathbf{\sigma_m})$ is a Gaussian in flux space.
This allows our ensemble of flows to approximate the distribution $p(z, \mathbf{m})$, where \mathbf{m} is the vector of true magnitudes for the galaxy.
For more details on training the ensemble, see Appendix~\ref{app:training-details}.

>>>>

For the training set, we use 100,000 galaxies from the catalog created in Section~\ref{sec:galaxy-catalog}.
Each galaxy in the training set has a true redshift and observed magnitudes in the $ugrizy$ bands, with corresponding photometric errors.
To account for the photometric error, at the start of each training epoch, we resample the training set from the photometric error distributions.
In other words, each epoch, for each galaxy, we sample
\begin{align}
    \mathbf{m} \sim p(\mathbf{\hat{m}}, \mathbf{\sigma_m}),
\end{align}
where $\mathbf{\hat{m}}$ are the observed magnitudes with photometric errors $\mathbf{\sigma_m}$, and $p(\mathbf{\hat{m}}, \mathbf{\sigma_m})$ is a Gaussian in flux space.
This allows our ensemble of flows to approximate the distribution $p(z, \mathbf{m})$, where $\mathbf{m}$ is the vector of true magnitudes for the galaxy.
For more details on training the ensemble, see Appendix~\ref{app:training-details}.
